Towards End-user Web Scraping For Customization

### 2021-05-11 paper.tex
Update HTML acknowledgements section as well

\section*{Acknowledgments}
Thank you to Gloria Lin, Joshua Pollock, the members of MIT's Software Design Group,
the anonymous reviewers of PX/21 and the particpants of PX/21 for providing valuable
feedback on this work. The authors gratefully acknowledge the support of the CNS division of the National Science Foundation
through award number 1801399.

>>>>

\section*{Acknowledgments}

Thank you to Gloria Lin, Joshua Pollock, the members of MIT's Software
Design Group, the anonymous reviewers of PX/21 and the particpants of
PX/21 for providing valuable feedback on this work. The authors
gratefully acknowledge the support of the CNS division of the National
Science Foundation through award number 1801399.
